First, I would like to thank my dissertation committee, Dr. Carlos Baiz, Dr. Ron Elber, Dr. Dmitrii Makarov, and Dr. Pengyu Ren, for their helpful discussions and encouragement throughout my graduate career. 
I would also like to thank Dr. Darrin Bellert and Dr. Kevin Chambliss at my undergraduate institute Baylor University for their encouragement and advice on pursuing a graduate education. 
I thank the Texas Advanced Computing Center for their computing resources that have been an integral part of all of my research projects. 

Next, I would like to thank the Webb group as a whole for being a wonderful group, providing valuable ideas and comments, and help pushing this research further. 
Specifically, I want to thank Joshua Slocum and Elisa Novelli for their tireless experimental work that provided the basis for many of these calculations. 
These collaborations have been the most exciting and rewarding part of my graduate career, which is due in no small part to their patience, scientific curiosity, genuine insight, and friendship.  

I would like to thank my advisor Dr. Lauren Webb for her mentorship over the last five years. 
Lauren has taught me everything I know about being an effective scientist and communicator. 
I'm extremely grateful to have been a part of such a friendly and collaborative lab group that has shaped the success of my graduate career. 
In particular, Josh, Elisa, Whitney and Cari are now all lifelong friends. 
Without them, I likely would not have finished this program. 
They have commiserated with me when times were tough, pushed me when deadlines were approaching, and encouraged me to take a break when I needed it. 

I would like to thank my family for their support and love, specifically my parents, Todd and Lisa. 
Without their encouragement, none of this work would have been possible.  
I thank my siblings Zach and Lindsay for their friendship and for being there when I needed anything. 
I thank my grandparents for their insistence on the importance of higher education and for their financial support when it was needed most. 

Finally, I would like to thank my wife Meredith, and our dog Mia, for standing by me through the last five years while I pursued this degree. 
Her encouragement and motivation has pushed me through the stressful moments and helped shape these past years into the best of my life. 
